\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenmes,dvipsnames]{color}
\usepackage{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{changepage}
\usepackage{fontawesome5}
\usepackage{graphicx}

\input{glyphtounicode}

\definecolor{yale}{HTML}{00356B}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\let\oldl\Large
\renewcommand{\Large}[1]{{\color{yale}\oldl{#1}}}

\let\oldsc\textsc{}
\renewcommand{\textsc}[1]{\normalsize\oldsc{#1}}


\newenvironment{desc}{\footnotesize \begin{adjustwidth}{15pt}{0pt}}
{\end{adjustwidth}}
\newcommand{\years}[2]{\footnotesize \ifx?#1?#2\else#1 -- #2\fi}

\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\titleformat{\section}{
  \color{yale}\vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\vspace{-1pt} \color{yale}\titlerule \vspace{-6pt}]


\newenvironment{module}[4]{
\textsc{#1} \hfill \textsc{\footnotesize#4}\\
\years{#2}{#3}
\footnotesize \begin{adjustwidth}{15pt}{0pt}
}{
\end{adjustwidth} 
\normalsize \null\vspace{-11pt}
}

\newenvironment{edmodule}[5]{
\textsc{#1} \hfill \textsc{\footnotesize#4}\\
\years{#2}{#3} \hfill \textsc{\footnotesize#5}
\footnotesize \begin{adjustwidth}{15pt}{0pt}
}{
\end{adjustwidth} 
\normalsize \null\vspace{-11pt}
}

\newenvironment{moduletwo}[2]{
\textsc{#1} \hfill \textsc{\footnotesize#2}
\footnotesize \begin{adjustwidth}{12pt}{0pt}
\setstretch{1.15}}{
\end{adjustwidth} \normalsize \null\vspace{-11pt}
}

\newcommand{\category}[1]{\textbf{\Large{#1}}\vspace{-5pt}\\ \setstretch{1.35}\null\vspace{-5pt}\newline}

\begin{document}
\setstretch{1.1}
\begin{center}
\begin{minipage}[t]{.3\textwidth}
\vspace{0pt}
\footnotesize
\reflectbox{\faIcon{phone}} (612) 868-3457\\
\faIcon{envelope} \href{mailto:jason.wang278@gmail.com}{\underline{jason.wang278@gmail.com}}\\%\faLink \href{https://jas0n.net}{\underline{github.com/piis31415}}
\end{minipage}
\begin{minipage}[t]{.35\textwidth}
\vspace{0pt}
\centering
\textbf{\color{yale}\Huge \scshape Jason Wang} 
\end{minipage}
\begin{minipage}[t]{.3\textwidth}
\vspace{0pt}
\footnotesize\begin{flushright}
\href{https://linkedin.com/in/jason-l-wang}{\underline{linkedin.com/in/jason-l-wang}} \faLinkedin\\
\href{https://github.com/piis31415}{\underline{github.com/piis31415}} \faGithub\end{flushright}
\end{minipage}
\end{center}\vspace{-10pt}\\
\hrulefill\vspace{-10pt}\\
\null\hrulefill\vspace{5pt}\\
\category{Education}
\begin{edmodule}{Yale University}{Sep. 2021}{May 2025}{New Haven, CT}{\textbf{Major:} Undecided, \textbf{GPA:} 3.76/4.00}
\end{edmodule}\vspace{-25pt}\footnotesize
\begin{itemize}\setstretch{1}
    \item \textbf{Relevant Coursework:} Probability Theory; Intensive Introductory Physics; Intro to CS; Intro to EE
    \item \textbf{Planned for Spring 2022:} Data Structures \& Programming Techniques; Real Analysis; Intro to Abstract Algebra 
\end{itemize}\\
\begin{edmodule}{University of Minnesota}{Sep. 2016}{May 2021}{Minneapolis, MN}{
\textbf{GPA:} 3.96/4.00}
\end{edmodule}\vspace{-25pt}
\begin{itemize}\setstretch{1}
    \item \textbf{Relevant Coursework:} Intro to Waves, Optics, and Special Relativity; Single- \& Multi-Variable Calculus; Linear Algebra; Error-Correcting Codes, Finite Fields, and Algebraic Curves; Cryptology; Dynamical Systems \& Chaos
\end{itemize}\vspace{-7pt}
%\begin{edmodule}{The Blake School}{Sep. 2017}{June 2021}{Minneapolis, MN}{
%\textbf{GPA:} 3.92/4.00}
%\end{edmodule}\\\vspace{-23pt}
%\begin{module}{Yale University}{Sep. 2021}{May 2025 (expected)}{New Haven, CT} \end{module}
\hrulefill\vspace{5pt}\\
\category{Experience}
\begin{module}{MNHSML, Yale Math Competitions / \footnotesize Math Competitor, Problem Writer}{Apr. 2016}{Present}{}
\end{module}\vspace{-25pt}
\begin{itemize}\setstretch{1}
    \item Organized virtual practices for 100+ math team members on Zoom. Created handouts, mock competition using \LaTeX. 
    \item Participated in competitions both individually (AIME, USAJMO, Putnam) and with a team (ARML, HMMT, PUMaC).
    \item Wrote problems for MMATHS 2021 for $\sim 500$ students.
\end{itemize}
\begin{module}{University Of Minnesota / \footnotesize Undergraduate Researcher}{Jan. 2020}{Present}{Minneapolis, MN} 
\end{module}\vspace{-25pt}
\begin{itemize}\setstretch{1}
    \item Investigated ranking \& rating systems and developed a metric to quantify gerrymandering in group of three undergraduates, led by post-doctorate Alexis Johnson.
    \item Used Python (pandas, matplotlib) to process raw government data and to develop \& calculate our metric.
    \item Presented at the MAA North Central Conference in March 2021, planned publication in 2022.
\end{itemize}
%\begin{module}{Yale University / \footnotesize Student Tech %Collaborative}{Oct. 2021}{Present}{New Haven, CT} 
%\vspace{5pt}
%\begin{itemize}\setstretch{1}
%    \item 
%\end{itemize}
%\end{module}
%\begin{module}{Student Tech Collaborative \\ \footnotesize Student Tech}{Oct. 2021}{Present}{Minneapolis, MN}
%\vspace{5pt}
%\begin{itemize}\setstretch{1}
%\item Founded a satirical news website for my high school. 
%\item Tinkered with an existing WordPress template's CSS to %customize website design 
%\item Implemented static website hosting using GitHub Pages
%\item Wrote numerous articles satirizing everything from school %administration to world events.
%\end{itemize}
%\end{module}
\vspace{-9pt}
\hrulefill\vspace{5pt}\\
\category{Projects}
\begin{module}{COVID Data Visualization}{Oct. 2020}{May 2021}{}
\end{module}\vspace{-25pt}
\begin{itemize}\setstretch{1}
    \item Used MN government data and Python (matplotlib) to create graphs of county COVID cases and infection rates.
    \item Shared findings with school administration, $\sim200$ followers on Instagram.
\end{itemize}
\begin{module}{CMIMC Programming Competition}{}{Jan. 2021}{}
\end{module}\vspace{-25pt}
\begin{itemize}\setstretch{1}
    \item Won 1st place in AI round, 8th place overall in the 2021 Carnegie Mellon Informatics and Mathematics Programming Competition with a team of three.
    \item Developed AI using Python in one week to play three adversarial AI games with other AIs developed by other teams.
\end{itemize}
\vspace{-25pt}
\null\hrulefill\vspace{5pt}\\
\category{Skills \& Interests}
\begin{moduletwo}{Technical}{}
C, Python (matplotlib, seaborn, numpy, pandas), JavaScript, \LaTeX, Racket, R, Unix
\end{moduletwo}
\vspace{-7pt}
\begin{moduletwo}{Languages}{}
Bilingual English and Mandarin Chinese, Limited French
\end{moduletwo}
\vspace{-7pt}
\begin{moduletwo}{Interests}{}
Music Composition, Cello, Piano, Cooking, Origami, Creative Writing
\end{moduletwo}
\end{document} 
